---
title: "Test template Rmarkdown"
author: "INSERT-YOUR-NAME-HERE"
date: "15 January 2026"
output: ## do not change anything here.
    html_document:
        code_download: true
---

# Problem 3

**3.1 Set data as panel data. **

```{r, message=FALSE, warning=FALSE}

# Insert R-code here

```

**3.2 Run a pooled OLS regression. What is the return of education? Assess whether it is statistically significant.**

```{r, message=FALSE, warning=FALSE}

# Insert R-code here

```

*Insert your answer here*

**3.3 Include individual-level fixed effects **

```{r, message=FALSE, warning=FALSE}

# Insert R-code here

```

**3.4 Estimate a random effects model. **

```{r, message=FALSE, warning=FALSE}

# Insert R-code here

```

**3.5 Interpret and compare the estimates of the three estimated models. **

*Insert your answer here*

**3.6 Run a Hausman test for fixed versus random effects model. What is your conclusion? **

```{r, message=FALSE, warning=FALSE}

# Insert R-code here

```

*Insert your answer here*
